---
title: "R Notebook"
output: html_notebook
---

Load libraries
```{r}
library(jsonlite)
library(data.table)
library(stringi)
library(e1071)
```

Load data and define debugging procedure
```{r}
rawTrainData <- fromJSON("data/train.json")
```

Load data table and transform data
```{r}
trainTable <- data.table(bathrooms = unlist(rawTrainData$bathrooms),
                         bedrooms = unlist(rawTrainData$bedrooms),
                         building_id = unlist(rawTrainData$building_id),
                         created = unlist(rawTrainData$created),
                         description = unlist(stri_length(rawTrainData$description)), #cleanup, word analysis
                         display_address = unlist(rawTrainData$display_address), #needs to be cleaned and word analysis performed
                         #features = unlist(rawTrainData$features), #analyze important features, count
                         latitude = unlist(rawTrainData$latitude),
                         listing_id = unlist(rawTrainData$listing_id),
                         longitude = unlist(rawTrainData$longitude),
                         manager_id = unlist(rawTrainData$manager_id),
                         #photos = unlist(length(rawTrainData$photos)), #include count for now, maybe size, resolution, lighting analysis in the future
                         price = unlist(rawTrainData$price),
                         street_address = unlist(rawTrainData$street_address), #find difference with display address, needs to be cleaned and word analysis performed
                         interest_level = unlist(rawTrainData$interest_level)
                         )

for (i in 1:49352) {
  trainTable$feature_count[i] <- length(unlist(rawTrainData$features[i]))
  trainTable$photo_count[i] <- length(unlist(rawTrainData$photos[i]))
  if (i %% 1000==0)
    print(i)
}

bkp <- trainTable
```

NOT USED ANYMORE. Create integer column for interest level
```{r}
trainTable$interest_level <- gsub("medium", "pmedium", trainTable$interest_level)
trainTable$interest_level <- gsub("high", "xhigh", trainTable$interest_level)
trainTable$interest <- as.numeric(factor(trainTable$interest_level, levels = sort(unique(trainTable$interest_level))))
trainTable$interest_level <- gsub("pmedium", "medium", trainTable$interest_level)
trainTable$interest_level <- gsub("xhigh", "high", trainTable$interest_level)
trainTable[,11:12]
```

Create integer columns for listing creation time
```{r}
trainTable$day_created <- as.POSIXlt(trainTable[[4]], format = "%Y-%m-%d %H:%M:%S")$mday
trainTable$hour_created <- as.POSIXlt(trainTable[[4]], format = "%Y-%m-%d %H:%M:%S")$hour
```

Create integer for manager
```{r}
trainTable
buildingTable <- as.data.frame(table(trainTable$building_id))
colnames(buildingTable) <- c("building_id", "building_id_freq")
buildingTable
trainTable <- merge(trainTable, buildingTable, by="building_id", all=TRUE)
trainTable
```

Create integer for manager
```{r}
trainTable
managerTable <- as.data.frame(table(trainTable$manager_id))
colnames(managerTable) <- c("manager_id", "manager_id_freq")
managerTable
trainTable <- merge(trainTable, managerTable, by="manager_id", all=TRUE)
trainTable
```

Create integer for display address
```{r}
trainTable
addrTable1 <- as.data.frame(table(tolower(trainTable$display_address)))
colnames(addrTable1) <- c("display_address", "display_address_id_freq")
addrTable1
trainTable$display_address_id_freq <- merge(trainTable, addrTable1, by="display_address", all=TRUE)
trainTable

trainTable <- within(trainTable, display_address_length <-length(display_address))
trainTable
```

NOT USED ANYMORE. Analyze features
```{r}
#numeric: bathrooms, bedrooms, latitude, longitude, price, interest, dayCreated, hourCreated
cor(trainTable[,c(1,2,6,8,10,12,13,14)])
plot(table(trainTable$bathrooms))
plot(table(trainTable$bedrooms))
plot(table(trainTable$interest))
plot(table(trainTable$dayCreated))
plot(table(trainTable$hourCreated))

min(trainTable$latitude); max(trainTable$latitude); mean(trainTable$latitude)
min(trainTable$longitude); max(trainTable$longitude); mean(trainTable$longitude)
min(trainTable$price); max(trainTable$price); mean(trainTable$price)
 #TODO: description, display_address, features, photos, street_address
```

NOT USED ANYMORE. Cleanup features
```{r}
#TODO: evaluate if this is necessary
names(trainTable)
plot(trainTable$bathrooms) #
plot(trainTable$bedrooms) #
plot(trainTable$latitude) #
plot(trainTable$longitude) #
plot(trainTable$price) #

temp.lm <- lm(interestClass~price, trainTable)
trainTable$cooks <- cooks.distance(temp.lm)
trainTable$student <- rstudent(temp.lm)
pairs(bedrooms + interestClass, data=trainTable)
trainTable[1]
plot(lm(interestClass~bathrooms, trainTable[(trainTable$cooks < 4/length(trainTable$cooks) & abs(trainTable$student) < 3)]))
max(trainTable[trainTable$cooks < 4/length(trainTable$cooks) & abs(trainTable$student) < 10]$bathrooms)
```


#First attempt
create training data tables for A,B,C
```{r}
#copy columns to new table
Atrain <- trainTable[1,c(3,4,6,8,10,13,14,12)]
```

SVM tunning, RBF Kernel, 36 hours
```{r}
Sys.time()
svm.tune1 <- tune(svm, train1[,1:7], train1$interest, kernel="radial", ranges=list(cost=2^c(-5,-1,1,5), gamma=2^c(-4,-6,-8)))
Sys.time()

plot(svm.tune1)
```

Train SVM, limited crossvalidation to 5, only two classes (0,1), grid tuned by previous grid search, 
```{r}
# create new dataset
train1_A <- within(train1, interest[interest != 1] <- 0)

Sys.time()
svm.tune1_A <- tune(svm, train.x=train1_A[,1:7], train.y=train1_A$interest, kernel="radial", ranges=list(cost=2^c(4.5,5.0,5.5), gamma=2^c(-4,-1,2)), tunecontrol = tune.control(cross=5))
Sys.time()
```

```{r}
trainMini <- within(train1, interest[interest != 3] <- "NOT HIGH")
trainMini <- within(trainMini, interest[interest == 3] <- "HIGH")

Sys.time()
svm.tuneMini <- tune.svm(x=trainMini[,1], y=factor(trainMini$interest), kernel="radial", scale=FALSE, cost=2^c(-6,-3,0,3,6), gamma=2^c(-10,-5,0,5), tunecontrol = tune.control(cross=3))
Sys.time()

minisvm <- svm(x=train1_A[,1:7], y=factor(train1_A$interest), kernel="radial", cost=svm.tune1_A$best.parameters$cost, gamma=svm.tune1_A$best.parameters$gamma, scale=FALSE)

predmini <- predict(minisvm, train[,1])

table(predmini, trainMini$interest)
```

