---
title: "R Notebook"
output: html_notebook
---

Load libraries
```{r}
library(jsonlite)
library(data.table)
library(e1071)
```

Load data and define debugging procedure
```{r}
rawTrainData <- fromJSON("data/train.json")

printEntryFromRawData <- function(index) {
  c(sprintf("Index %d", index),
    rawTrainData$bathrooms[index],
    rawTrainData$bedrooms[index],
    rawTrainData$building_id[index],
    rawTrainData$created[index],
    rawTrainData$description[index],
    rawTrainData$display_address[index],
    rawTrainData$features[index],
    rawTrainData$latitude[index],
    rawTrainData$listing_id[index],
    rawTrainData$longitude[index],
    rawTrainData$manager_id[index],
    rawTrainData$photos[index],
    rawTrainData$price[index],
    rawTrainData$street_address[index],
    rawTrainData$interest_level[index]
    )
}

printEntryFromRawData(9464)

```

Load data table and transform data
```{r}
trainTable <- data.table(bathrooms = unlist(rawTrainData$bathrooms),
                         bedrooms = unlist(rawTrainData$bedrooms),
                         building_id = unlist(rawTrainData$building_id),
                         created = unlist(rawTrainData$created),
                         description = unlist(rawTrainData$description), #cleanup, word analysis
                         #display_address = unlist(rawTrainData$display_address), #needs to be cleaned and word analysis performed
                         #features = unlist(rawTrainData$features), #analyze important features, count
                         latitude = unlist(rawTrainData$latitude),
                         listing_id = unlist(rawTrainData$listing_id),
                         longitude = unlist(rawTrainData$longitude),
                         manager_id = unlist(rawTrainData$manager_id),
                         #photos = unlist(rawTrainData$photos), #include count for now, maybe size, resolution, lighting analysis in the future
                         price = unlist(rawTrainData$price),
                         #street_address = unlist(rawTrainData$street_address), #find difference with display address, needs to be cleaned and word analysis performed
                         interest_level = unlist(rawTrainData$interest_level)
                         )
```

Create integer column for interest level
```{r}
trainTable$interest_level <- gsub("medium", "pmedium", trainTable$interest_level)
trainTable$interest_level <- gsub("high", "xhigh", trainTable$interest_level)
trainTable$interest <- as.numeric(factor(trainTable$interest_level, levels = sort(unique(trainTable$interest_level))))
trainTable$interest_level <- gsub("pmedium", "medium", trainTable$interest_level)
trainTable$interest_level <- gsub("xhigh", "high", trainTable$interest_level)
trainTable[,11:12]
```

Create integer columns for listing creation time
```{r}
trainTable$dayCreated <- as.POSIXlt(trainTable[[4]], format = "%Y-%m-%d %H:%M:%S")$mday
trainTable$hourCreated <- as.POSIXlt(trainTable[[4]], format = "%Y-%m-%d %H:%M:%S")$hour
```

Analyze features
```{r}
#numeric: bathrooms, bedrooms, latitude, longitude, price, interest, dayCreated, hourCreated
cor(trainTable[,c(1,2,6,8,10,12,13,14)])
plot(table(trainTable$bathrooms))
plot(table(trainTable$bedrooms))
plot(table(trainTable$interest))
plot(table(trainTable$dayCreated))
plot(table(trainTable$hourCreated))

min(trainTable$latitude); max(trainTable$latitude); mean(trainTable$latitude)
min(trainTable$longitude); max(trainTable$longitude); mean(trainTable$longitude)
min(trainTable$price); max(trainTable$price); mean(trainTable$price)
 #TODO: description, display_address, features, photos, street_address
```

Cleanup features
```{r}
#TODO: evaluate if this is necessary
names(trainTable)
plot(trainTable$bathrooms) #
plot(trainTable$bedrooms) #
plot(trainTable$latitude) #
plot(trainTable$longitude) #
plot(trainTable$price) #

temp.lm <- lm(interestClass~price, trainTable)
trainTable$cooks <- cooks.distance(temp.lm)
trainTable$student <- rstudent(temp.lm)
pairs(bedrooms + interestClass, data=trainTable)
trainTable[1]
plot(lm(interestClass~bathrooms, trainTable[(trainTable$cooks < 4/length(trainTable$cooks) & abs(trainTable$student) < 3)]))
max(trainTable[trainTable$cooks < 4/length(trainTable$cooks) & abs(trainTable$student) < 10]$bathrooms)
```


#First attempt
Scale data
```{r}
#copy columns to new table
train1 <- trainTable[,c(1,2,6,8,10,13,14,12)]

#scale values
range.max = 1; range.min = -1
maxValue = max(train1$bathrooms); minValue = min(train1$bathrooms)
train1$bathrooms = (range.max - range.min) * (train1$bathrooms - minValue) / (maxValue - minValue) + range.min

maxValue = max(train1$bedrooms); minValue = min(train1$bedrooms)
train1$bedrooms = (range.max - range.min) * (train1$bedrooms - minValue) / (maxValue - minValue) + range.min

maxValue = max(train1$latitude); minValue = min(train1$latitude)
train1$latitude = (range.max - range.min) * (train1$latitude - minValue) / (maxValue - minValue) + range.min

maxValue = max(train1$longitude); minValue = min(train1$longitude)
train1$longitude = (range.max - range.min) * (train1$longitude - minValue) / (maxValue - minValue) + range.min

maxValue = max(train1$price); minValue = min(train1$price)
train1$price = (range.max - range.min) * (train1$price - minValue) / (maxValue - minValue) + range.min

maxValue = max(train1$dayCreated); minValue = min(train1$dayCreated)
train1$dayCreated = (range.max - range.min) * (train1$dayCreated - minValue) / (maxValue - minValue) + range.min

maxValue = max(train1$hourCreated); minValue = min(train1$hourCreated)
train1$hourCreated = (range.max - range.min) * (train1$hourCreated - minValue) / (maxValue - minValue) + range.min

#numeric: bathrooms, bedrooms, latitude, longitude, price, dayCreated, hourCreated, interest
```

SVM tunning, RBF Kernel, 36 hours
```{r}
Sys.time()
svm.tune1 <- tune(svm, train1[,1:7], train1$interest, kernel="radial", ranges=list(cost=2^c(-5,-1,1,5), gamma=2^c(-4,-6,-8)))
Sys.time()

plot(svm.tune1)
```

Train SVM, limited crossvalidation to 5, only two classes (0,1), grid tuned by previous grid search, 
```{r}
# create new dataset
train1_A <- within(train1, interest[interest != 1] <- 0)

Sys.time()
svm.tune1_A <- tune(svm, train.x=train1_A[,1:7], train.y=train1_A$interest, kernel="radial", ranges=list(cost=2^c(5,7,9,11), gamma=2^c(-4,-1,2)), tunecontrol = tune.control(cross=5))
Sys.time()
```

